Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-10-01 manuscript/main.tex
typo in manuscript
reformatted bibliography

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
    \caption{Coefficients of quantile regression for alignment score on
    ideological distance. Dots indicate the point estimate. Horizontal bar
represent 95\% confidence intervals obtained with clustered bootstrap. 
Note that the x-axis is not in a natural scale.}
    \label{fig:quantile_regression}
\end{figure}

@@

\bibliographystyle{chicago}
\bibliography{bibliography}

@@

\begin{enumerate}
\item There are four options for $F_1$ (Gap in $\mathcal{A}$, Gap in
    $\mathcal{B}$, Mismatch, Match) . This alignment is optimal when $S(F_1)$ is maximized
\item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element. If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
\item By induction therefore follows that every alignment represented in the
    dynamic programming matrix (\ref{fig:score_matrix}) and calculated according
        to Equations \ref{eqn:scoring} and \ref{eqn:fill} is an optimal alignment
    ending in the locations specified by the row and column index in the matrix.
\item The dynamic programming matrix contains all possible alignments. Since
    every cell is optimal, the highest score in the matrix must be globally
    optimal.
\end{enumerate}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
    \caption{Coefficients of quantile regression for alignment score on
    ideological distance. Dots indicate the point estimate. Horizontal bar
represent 95\% confidence intervals obtained with clustered bootstrap. 
Note that the y-axis is not in a natural scale.}
    \label{fig:quantile_regression}
\end{figure}

@@

\bibliographystyle{authoryear1}
\bibliography{bibliography}

@@

\begin{enumerate}
\item There are four options for $F_1$ (Gap in $\mathcal{A}$, Gap in
    $\mathcal{B}$, Mismatch, Match) . This alignment is optimal when $S(F_1)$ is maximized
\item Every alignment's score $S(F_i)$ with $i > 1$ when maximized, is composed of the score of the `one-shorter' alignment $S(F_{i-1})$ and the score of the $i$-th element. If not the score could be increased by choosing a different $F_{i-1}$ that has a higher score.
\item By induction therefore follows that every alignment represented in the
    dynamic programming matrix (Figure \ref{fig:score_matrix}) and calculated according
        to Equations \ref{eqn:scoring} and \ref{eqn:fill} is an optimal alignment
    ending in the locations specified by the row and column index in the matrix.
\item The dynamic programming matrix contains all possible alignments. Since
    every cell is optimal, the highest score in the matrix must be globally
    optimal.
\end{enumerate}
